Notes on data anlaysis

### 2020-06-30 Code/Rmd/data_analysis_notes.Rmd
First version of the Introduction and Methods, and second version of the ICIS 2020 poster

>>>>

## Limitations

* Cross-sectional data for longitudinal claims
* Data is right censored    
* Inventory:
    - Phonological forms?
    - We can't say how frequently words are produced by the parents or the toddler.
    - Although instructed to ignore imitations, it is difficult to say whether a toddler has *really* acquired a word that produces, or she can only imitate it.
    - Responses in the questionnaire rely heavily on parental memory.
    - We don't know about the context at which words are heard or produced.
    - Classification system of items (e.g., *household items*) is adult centric. Children may use the words *pretty* to name jewellery [@bates1994].
* Mid and mid-upper class families are overrepresented in the sample.
